TBD

### 2020-10-31 outputs/paper/paper.Rmd
Update paper.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
```

@@

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.

@@

Our data is of penguins (Figure \@ref(fig:bills)).

```{r bills, fig.cap="Bills of penguins", echo = FALSE}
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)

```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}

# This needs to be about the random data tha tI sasmpled?
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk way more about it.

@@

First, we train a multilevel logistic regression model using raw data from DATA towards the variable of interest using our x explanatory variables. We then apply this model to our post-stratification data set to get the estimates.

@@

In our case, we want to estimate $\beta_{age},\beta_{education},\beta_{race},\beta_{income},\beta_{state}$ in \@ref(eq:logvar).

\begin{equation}
log(\frac{p}{1-p})=\beta_0+\beta_{age}x_{age}
+\beta_{education}x_{education}+\beta_{race}x_{race}
+\beta_{income}x_{income}+\beta_{state}x_{state}(\#eq:logvar)
\end{equation}

where p is the probability that the respondent votes for Trump, $\beta_0$ is the intercept, $\beta_{age}$ is the parameter for age, $\beta_{education}$ is the parameter for education level, $\beta_{race}$ is the parameter for race, $\beta_{income}$ is the parameter for income, and $\beta_{state}$ is the parameter for the state the respondent is in.

The logic behind post-stratification is that we divide the sample data into strata based on a few attributes such as state, income, education level. Then we come up with a weight for each stratum to adjust its influence towards our prediction. Namely, if a stratum is over-represented, we want to reduce its impact on the result; if a stratum is under-represented, we want to increase its influence.
We need a post-stratification dataset that is large enough to do this. In this report, we use the ACS(reason).

The post-stratification estimate is defined by $\hat{y}_{PS} = \frac{\sum{N_j\hat{y}_j}}{\sum{N_j}}$ where $\hat{y}_j$ is the estimate of y in cell j, and $N_j$ is the size of the j-th cell in the population.

Notably, the multilevel regression before post-stratification produces a proportion for the post-stratification based on regression, instead of merely averaging the sample in each stratum.

We fit two nested multilevel logistic regressions for estimating candidate support in each cell.

*Formula of the first model

That is the probability that a respondent has the intention to vote for either Trump or Biden.

And the second model predicts:

**Formula of the second model

That is the probability that a respondent has the intention to vote for Trump, given that he/she either has the intention to vote for Trump or Biden.

Together, mod1 and mod2 form a Bayesian model to predict whether Donald Trump will win the election.

@@

@@

Weaknesses and next steps should also be included.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

@@

@@

@@

First, we train a multilevel logistic regression model using raw data obtained from the voter study group towards the variable of interest using the 7 explanatory variables. We then apply this model to our post-stratification data set to get the estimates.

@@

The logic behind post-stratification is that we divide the sample data into strata based on a few attributes such as state, income, education level. Then we come up with a weight for each stratum to adjust its influence towards our prediction. Namely, if a stratum is over-represented, we want to reduce its impact on the prediction result; if a stratum is under-represented, we want to increase its influence.
We need a post-stratification dataset that is large enough to do this. In this report, we use the ACS(reason).

The post-stratification estimate is defined by $\hat{y}_{PS} = \frac{\sum{N_j\hat{y}_j}}{\sum{N_j}}$ where $\hat{y}_j$ is the estimate of y in cell j, and $N_j$ is the size of the j-th cell in the population. An illustration using the education variable is $\hat{y}_{edu}^{PS} = \frac{\sum_{j\in J_{edu}}{N_j\hat{y}_j}}{\sum_{j\in J_{edu}}{N_j}}$, we can get an estimation given any level of education of respondents, $J_{edu}$ denotes all subsets of education levels, $\cup_{i\in J} J^{edu}_{i} =$ all possible education levels.

The multilevel regression before post-stratification produces a proportion for the post-stratification based on regression, instead of merely averaging the sample in each stratum. Specifically, all possible combinations of cells are from combining:

-
-
-
-
-
-

We fit the logistic regressions for estimating candidate support in each cell. We used `function` from `package` to fit \@ref(eq:model).

\begin{equation}
P(Trump) = logit^{-1}(
\beta_0 + \beta_age + \beta_{j[i]}^{edu} + \beta_{j[i]}^{race}
+ \beta_{j[i]}^{income} + \beta_{j[i]}^{state} + \beta_{j[i]}^{mask}
) (\#eq:model)
\end{equation}

\@ref(eq:model) is the model that we fit using the survey data, with $\beta_{j[i]}^{var} \sim N(0, \sigma^2_{var})$. 
$\beta_0$ is the intercept,each of $\beta_{j[i]}^{var}$ represents the parameter for the i-th respondent in j-th cell. For example, $\beta_{j[i]}^{state}$ can take values from $\beta$ for all states in the US. Then the model sums up estimates for each cell to the population.

We find the mask parameter interesting, firstly because US is the country with the most COVID cases in the world, the influence of COVID on election choices is inevitable. Secondly, since Trump and Biden have very opposites towards the pandemic and how to handle it, this parameter will likely represent part of respondent's voting intention in the same way as any more common political indicators.

@@

```{r}
fit <- stan_glmer(#try using glmer()
  binary ~ factor(male) + factor(male) * factor(age) +
    (1 | state) + (1 | age) + (1 | eth) + (1 | income),
  family = binomial(link = "logit"),
  data = clean_survey#all age, state etc coming from post-strat
)
```

```{r}
# to get the estimated proportions and associated 95% PIs by state
res_state <- fit %>%
  add_predicted_draws(newdata=state_prop %>% 
                        filter(age_group>20, age_group<80, decade_married>1969),
                      allow_new_levels=TRUE) %>%
  rename(kept_name_predict = .prediction) %>% 
  mutate(kept_name_predict_prop = kept_name_predict*prop) %>% 
  group_by(state_name, .draw) %>% 
  summarise(kept_name_predict = sum(kept_name_predict_prop)) %>% 
  group_by(state_name) %>% 
  summarise(mean = mean(kept_name_predict), 
            lower = quantile(kept_name_predict, 0.025), 
            upper = quantile(kept_name_predict, 0.975))
```

```{r}
# graph by state
res_state %>% 
  arrange(-mean) %>% 
  left_join(d %>%
              group_by(state_name, kept_name) %>%
              summarise(n = n()) %>%
              group_by(state_name) %>%
              mutate(prop = n/sum(n)) %>%
              filter(kept_name==1)) %>% 
  ggplot(aes(y = mean, x = forcats::fct_inorder(state_name), color = "MRP estimate")) + 
  geom_point() +
  coord_flip() + 
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0) + 
  ylab("proportion keeping maiden name") + 
  xlab("state") + 
  geom_point(aes(state_name, prop, color = "raw data")) +
  scale_color_manual(name = "", values = c("MRP estimate" = "black", "raw data" = "red")) + 
  theme_bw() +
  ggtitle("Proportion of women keeping maiden name after marriage")

res_state %>% 
  mutate(statename = str_to_title(state_name)) %>% 
  #mutate(statename = ifelse(state_name=="district of columbia", "District of Columbia", statename)) %>% 
  ggplot(aes(fill = mean, state = statename)) + 
  geom_statebins() +
  scale_fill_viridis_c(name = "proportion keeping name") +
  theme_void()
ggsave("state_plot.png", width = 8, height = 6)
```

@@

### 1: Nested Bayesian Model /,
